\begin{enumerate}
\item Hinrichsen, Peter. 2015. "Analysis of Bi and Trifilar Oscillations.".\url{https://www.researchgate.net/publication/277404917_Analysis_of_Bi_and_Trifilar_Oscillations}.
\item Hinrichsen, Peter. 2016. "Trifilar Suspension Centering Correction." \url{https://www.researchgate.net/publication/303614060_Trifilar_Suspension_Centering_Correction}.
\item Du Bois, Jonathan $\&$ Lieven, Naj $\&$ Adhikari, Sondipon. 2009. "Error Analysis in Trifilar Inertia Measurements. Experimental Mechanics". \url{https://www.researchgate.net/publication/226018805_Error_Analysis_in_Trifilar_Inertia_Measurements}.
\item ckit. n.d. "Belt Tension Theory: Factors". Accessed May 29,2020. \url{https://www.ckit.co.za/secure/conveyor/troughed/belt_tension/belt_tension_factors.htm}.
\item Howard, Ian. 2020. Moment of inertia experiemental results. Dataset. Curtin University. \\ \url{https://lms.curtin.edu.au/bbcswebdav/pid-7423774-dt-content-rid-43761563_1/xid-43761563_1}
\item Howard, Ian. 2020. Belt Friction experiemental results. Dataset. Curtin University. \\ \url{https://lms.curtin.edu.au/bbcswebdav/pid-7423772-dt-content-rid-43761564_1/xid-43761564_1}
\item Howard, Ian. 2020. "Epicyclic Gear Lab Demonstration Video". Video. Curtin University Machine Dynamics BlackBoard.
\item Howard, Ian. 2020. "MassMomentOfInertia Part A - CompoundPendulumExperiment". mp4 video. Curtin University Machine Dynamics BlackBoard.
\item Howard, Ian. 2020. "MassMomentOfInertia Part B - TriFilar Suspension". mp4 video. Curtin University Machine Dynamics BlackBoard.
\item Howard, Ian. 2020. "Experimental Error Analysis Video". Video. Curtin University Machine Dynamics BlackBoard.
\item Howard, Ian. 2020. "Belt Friction Demostration Laboratory Video". Video. Curtin University Machine Dynamics BlackBoard.
\end{enumerate}